Journal Article Sampling Methodology

### 2016-12-07 src/README.Rmd
add first two articles to list

>>>>

(Morphological and biochemical responses of five tobacco cultivars to simultaneous infection with Pythium aphanidermatum and Meloidogyne incognita
Mujeebur Rahman KHAN, Ziaul HAQUE)[http://www.fupress.net/index.php/pm/article/view/11386]
(The Periplasmic PDZ Domain–Containing Protein Prc Modulates Full Virulence, Envelops Stress Responses, and Directly Interacts with Dipeptidyl Peptidase of Xanthomonas oryzae pv. oryzae)[http://apsjournals.apsnet.org/doi/abs/10.1094/MPMI-08-13-0234-R]
